---
title: "Generating Results Tables"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Generating Results Tables}
  %\usepackage[utf8]{inputenc}
---

The easiest way to create a report of frequency tables from a Qualtrics survey file and CSV response
dataset is to use QualtricsTools' `make_results_tables` function. 

```{r}
library(QualtricsTools)
# Let's use get_setup to load a sample survey.
get_setup(sample_data=TRUE)
# Using make_results_tables without definining the qsf_path or csv_path 
# parameters causes the function to retrieve the necessary survey data from 
# the global scope if all necessary objects are present. 
make_results_tables()
```

In this next example, I'm downloading a sample survey with responses as a 
QSF and CSV from the GitHub repository and then passing them 
as arguments to the make_results_tables function. 

```{r}
library(RCurl)

# Grab the sample data from our repository.
qsf <- getURL("https://raw.githubusercontent.com/emmamorgan-tufts/QualtricsTools/master/data/Sample%20Surveys/Better%20Sample%20Survey/Better_Sample_Survey.qsf")
csv <- getURL("https://raw.githubusercontent.com/emmamorgan-tufts/QualtricsTools/master/data/Sample%20Surveys/Better%20Sample%20Survey/Better_Sample_Survey.csv")

# Write the sample data to file.
qsf_tempfile_path = tempfile()
csv_tempfile_path = tempfile()
write(x = qsf, file = qsf_tempfile_path)
write(x = csv, file = csv_tempfile_path)

make_results_tables(
  qsf_path = qsf_tempfile_path,
  csv_path = csv_tempfile_path, 
  headerrows = 3
)
```

Of course, `make_results_tables` still does more than this. It allows users to specify their chosen output directory and desired output filename. In fact, `make_results_tables` automatically uses the file 
extension of the passed `filename` parameter to tell the `pandoc` program what format to convert the document into when rendering it. 


```{r}
output_filepath <- make_results_tables(
  qsf_path = qsf_tempfile_path,
  csv_path = csv_tempfile_path, 
  headerrows = 3,
  output_dir = tempdir(),
  filename = "ExampleHTMLFile.html"
)

requireNamespace("htmltools")
htmltools::includeHTML(output_filepath)
```

