---
title: "Sample Data included with QualtricsTools"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Sample-Surveys}
  %\usepackage[utf8]{inputenc}
---

There are several distinct surveys with sample response data included
in the QualtricsTools package repository. The easiest way to access a 
set of sample data is to pass `sample_data=TRUE` to `get_setup`.
```{r sample_data}
library(QualtricsTools)
get_setup(sample_data=TRUE)
ls(envir=globalenv())
```

Under the covers, the `get_setup(sample_data=TRUE)` function 
call is directly loading the sample data saved in Rda files inside
the `/data/` directory. Don't worry about understanding the construction of the 
`list.files.github` function that follows; it's just a tool I'm using 
to list files from the GitHub repository to show off the data that's 
included in the repository.
```{r}
library(httr)

list.files.github <- function(username = 'emmamorgan-tufts', repository = "QualtricsTools") {
    requireNamespace("httr")
    url <- paste0("https://api.github.com/repos/", username, "/", repository, "/git/trees/master?recursive=1", collapse="")
    req <- GET(url)
    stop_for_status(req)
    filelist <- unlist(lapply(content(req)$tree, "[", "path"), use.names = F)
    return(filelist)
}

qualtricstools_files <- list.files.github()
grep("^data/[^/]*$", qualtricstools_files, value = TRUE, perl = TRUE)
```

However, there is more data contained in the `/data` directory than just the rda files listed above. "Sample Surveys" listed above is a directory which contains 
many more sample surveys and response datasets as QSF and CSV files. 

```{r}
# Let's get the directories inside the Sample Surveys folder:
grep("^data/Sample Surveys/[^/]*$", qualtricstools_files, value = TRUE, perl = TRUE)
```

Each of these surveys and their corresponding response data can be downloaded from either the [GitHub repository](https://github.com/emmamorgan-tufts/QualtricsTools). Further, some surveys like the 
"Comment Coding" survey include extra data or extra formatting which are meant to test some of the 
more subtle features of QualtricsTools. If you clone the repository, then these files will also be
available in the `/data` folder, but if `devtools::install_github('emmamorgan-tufts/QualtricsTools')`
was used to install QualtricsTools, then these sample surveys will not be available in the 
locally installed version. 

```{r}
list.files( file.path(path.package("QualtricsTools"), "data/"))
```
